---
title       : Course Project
subtitle    : Shiny Application and Reproducible Pitch
author      : Josh Kennedy
job         : Pitch Consultant
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : solarized_light      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
ext_widgets : {rCharts: [libraries/nvd3]}
---
## Course Project
1. This is the final presentation for the COurse Project of the "Developing data products" course
2.   This course is part of the "Data Science specialization"
3. The project consists in two activities:
  -  Create a Shiny application
  -  Create a presentation in Slidify or Rstudio Presenter to pitch for the application.



--- .
## Introduction
- Interactive web application framework for R
- Create and share applications with others
- Open Source (GPL v3) R package
- Expects no knowledge of web technologies like HTML, CSS, or JavaScript.
- Can create autonomous webpages, or embedded interactive widgets in markdown
- A shiny app consist of two parts. A user Interface and a server

```{r, echo=FALSE}
str(iris)
```


--- .
## Interactive application
Figure's display in the last slide comes from the shiny app

https://kennej18.shinyapps.io/Temp1_project/

--- .
## Conclusion

Summary of results
```{r,echo=FALSE}
summary(iris)
```






